Network Configuration Synthesis with Abstract Topologies

### 2016-11-12 paper/abstraction/paper.tex
update concretization section

%By combining the tagging, filtering and preference mechanisms, we can generate safe BGP configurations. In general, configurations are generated by combining the per-prefix configurations in the same order specified in the policy.
Figure~\ref{fig:bgp-configs} shows part of the final configuration for spine routers for the concrete and abstract policies in a vendor-neutral syntax.
%
For prefix $\True$ ($0.0.0.0/[0..32]$), the spine routers will match advertisements from peer N1 and N2. The match for N1 is preferred since it has a higher BGP local-preference attribute (110). If an advertisement from N1 is available the spine uses this and attaches the community tag $(1,0)$ before sending the route to all its peers ($*$). If an advertisement is only available from the backup N2, then it attaches the tag $(0,1)$ instead.
%
The template configuration matches any global prefix $\CD{\$GP}$ from any internal peer and re-advertises the route to all of its peers. For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers. The concrete configurations have a similar configuration for each local and global prefix.

@@

One observation is that the spine template configuration and concrete spine configurations are structured similarly. We formalize this idea by defining a simple, vendor-neutral language for BGP configurations called \mbgp and formally define compilation for policies over both concrete and abstract topologies to \mbgp. In addition we define a two concretization ($con$) functions that translates an abstract \sysname policy and \mbgp configuration to a concrete \sysname policy and concrete \mbgp configuration respectively. Concretization takes a context $\Gamma : \mathit{Var} \rightarrow 2^{\mathit{Prefix} \times V}$ that maps each template variable to a set of pairs of a concrete prefix and topology location where the prefix is owned. The main theoretical result is that the compilation and concretization functions commute. More specifically:

>>>>

%By combining the tagging, filtering and preference mechanisms, we can generate safe BGP configurations. In general, configurations are generated by combining the per-prefix configurations in the same order specified in the policy.
Figure~\ref{fig:bgp-configs} (left) shows part of the final configuration for spine routers for the concrete and abstract policies in a vendor-neutral syntax.
%
For prefix $\True$ ($0.0.0.0/[0..32]$), the spine routers will match advertisements from peer N1 and N2. The match for N1 is preferred since it has a higher BGP local-preference attribute (110). If an advertisement from N1 is available the spine uses this and attaches the community tag $(1,0)$ before sending the route to all its peers ($*$). If an advertisement is only available from the backup N2, then it attaches the tag $(0,1)$ instead.
%
The template configuration matches any global prefix $\CD{\$GP}$ from any internal peer and re-advertises the route to all of its peers. For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers. The concrete configurations have a similar configuration for each local and global prefix.

@@

One observation is that the spine template configuration and concrete spine configurations are structured similarly. We formalize this idea by defining a simple, vendor-neutral language for BGP configurations called \mbgp and formally define compilation for policies over both concrete and abstract topologies to \mbgp. In addition we define a two concretization ($con$) functions that translates an abstract \sysname policy and \mbgp configuration to a concrete \sysname policy and concrete \mbgp configuration respectively. Concretization takes a context $\Gamma : \mathit{Var} \rightarrow 2^{\mathit{Prefix} \times V}$ that maps each template variable to a set of pairs of a concrete prefix and topology location where the prefix is owned. Intuitively, the spine template in concretized by replacing each abstract role with the set of all concrete routers that map to that role and each prefix template variable with a new entry in the configuration for each individual prefix provided by the context $\Gamma$.
The main theoretical result is that the compilation and concretization functions commute:
